Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-07-14 manuscript/manuscript.tex
Fixed wrong single column equation
Added figure spherical-shell reference in text

Lets consider a spherical shell with inner and outer radii $R_1$ and $R_2$, respectivetly, which density depends on the radius spherical coordinate.
The gravity potential generated by the shell on an arbitrary external point $Q(0,0,r)$ located along the $z$ axe at a distance $r$ can be written as follows:

@@

\iftwocol{
\begin{equation}
    \begin{split}
        V_\text{sh}^\text{exp}(r) = \frac{4\pi G}{r} 
        Ab \, e^{-\frac{\Delta h}{b}} \Big[ 
        & (R_2^2 - 2R_2 b + 2b^2)e^\frac{R_2}{b} - \\
        & (R_1^2 - 2R_1 b + 2b^2)e^\frac{R_1}{b} \Big].
    \end{split}
\end{equation}
}{
\begin{equation}
    V_\text{sh}^\text{sh}^\text{exp}(r) = \frac{4\pi G}{r} 
    Ab \, e^{-\frac{\Delta h}{b}} \left[ 
    (R_2^2 - 2R_2 b + 2b^2)e^\frac{R_2}{b} - 
    (R_1^2 - 2R_1 b + 2b^2)e^\frac{R_1}{b} \right].
\end{equation}
}

>>>>

Lets consider a spherical shell with inner and outer radii $R_1$ and $R_2$, respectivetly, which density depends on the radius spherical coordinate (Figure \ref{fig:spherical-shell}).
The gravity potential generated by the shell on an arbitrary external point $Q(0,0,r)$ located along the $z$ axe at a distance $r$ can be written as follows:

@@

\iftwocol{
\begin{equation}
    \begin{split}
        V_\text{sh}^\text{exp}(r) = \frac{4\pi G}{r} 
        Ab \, e^{-\frac{\Delta h}{b}} \Big[ 
        & (R_2^2 - 2R_2 b + 2b^2)e^\frac{R_2}{b} - \\
        & (R_1^2 - 2R_1 b + 2b^2)e^\frac{R_1}{b} \Big].
    \end{split}
\end{equation}
}{
\begin{equation}
    V_\text{sh}^\text{exp}(r) = \frac{4\pi G}{r} 
    Ab \, e^{-\frac{\Delta h}{b}} \left[ 
    (R_2^2 - 2R_2 b + 2b^2)e^\frac{R_2}{b} - 
    (R_1^2 - 2R_1 b + 2b^2)e^\frac{R_1}{b} \right].
\end{equation}
}
